ANOVA Comparison Simulations: Gaussian Data

### 2016-12-07 simulations/simulation.Rmd
Add 2 by 2 power plot to normal simulations

>>>>

```{r final_summary, fig.align = "center"}
#plots4 <- lapply(list(p1, p2, p4, p5), function(pl) pl + theme(legend.position = "none") + ggtitle(""))
#do.call(grid.arrange, plots4)

powers <- list(design1_power %>% as.data.frame() %>% mutate("Treatment" = rep("Constant Additive Effect", nrow(design1_power)), "Errors" = rep("Gaussian", nrow(design1_power))), 
               design2_power %>% as.data.frame() %>% mutate("Treatment" = rep("Single Site Effect", nrow(design2_power)), "Errors" = rep("Gaussian", nrow(design2_power))), 
               design3_power %>% as.data.frame() %>% mutate("Treatment" = rep("Constant Additive Effect", nrow(design3_power)), "Errors" = rep("Heavy-tailed", nrow(design3_power))), 
               design4_power %>% as.data.frame() %>% mutate("Treatment" = rep("Single Site Effect", nrow(design4_power)), "Errors" = rep("Heavy-tailed", nrow(design4_power))))

all_power_curves <- do.call(rbind, powers)
twobytwo <- melt(all_power_curves, id.vars = c("Treatment", "Errors")) %>% 
  mutate("pvalue" = rep((1: 100)/100, 5*4)) %>%
  mutate("Method" = variable) %>%
  ggplot(aes_string(x = "pvalue", y = "value", color = "Method")) +
  geom_line() +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  xlab("P-value") +
  ylab("Power") +
  facet_wrap(Treatment~Errors) +
  ggtitle("Gaussian Data")

twobytwo
```
